\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-08 paper.qmd
Updated Figure 7

plot_predict_umap_two_curvy <- ggplot(
  data = jittered_points_df, 
  aes(x = UMAP1,
      y = UMAP2)) +
  geom_point(alpha = 0.5) +
  interior_annotation("c", c(0.08, 0.93), cex = 2)
```

@@

```{r}
#| echo: false
#| label: fig-predict-two-curvy
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10
#| out-height: 80%
#| fig-cap: "Comparison of prediction generated using the exiting `umap` R package's prediction method and our method: (a) A view of the true model in projection from $7\\text{-}D$, (b) predicted data from the `umap` prediction method, (c) predicted data from our method, and (d) comparison of predictions from both methods. In plot (d), points representing the same data but predicted by different methods are connected by lines. Both prediction methods work similarly within the clusters, as each method predicts the data within the cluster with slight differences."

proj_plot_two_curvy_true + plot_predict_umap_fun_two_curvy +plot_predict_umap_two_curvy +
  plot_predict_umap_connect_two_curvy +
  plot_layout(ncol = 2)
```

>>>>

plot_predict_umap_two_curvy <- ggplot(
  data = true_pred_df, 
  aes(x = pred_UMAP_1,
      y = pred_UMAP_2)) +
  geom_point(alpha = 0.5) +
  interior_annotation("c", c(0.08, 0.93), cex = 2)
```

@@

```{r}
#| echo: false
#| label: fig-predict-two-curvy
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10
#| out-height: 80%
#| fig-cap: "Comparison of prediction generated using the exiting `umap` R package's prediction method and our method: (a) A view of the true model in projection from $7\\text{-}D$, (b) predicted data from the `umap` prediction method, and (c) predicted data from our method."

proj_plot_two_curvy_true + plot_predict_umap_fun_two_curvy +plot_predict_umap_two_curvy +
  plot_layout(ncol = 3)
```

### 2024-10-08 paper.tex
Update Fig10
Updated Figure 7

\caption{\label{fig-predict-two-curvy}Comparison of prediction generated
using the exiting \texttt{umap} R package's prediction method and our
method: (a) A view of the true model in projection from \(7\text{-}D\),
(b) predicted data from the \texttt{umap} prediction method, (c)
predicted data from our method, and (d) comparison of predictions from
both methods. In plot (d), points representing the same data but
predicted by different methods are connected by lines. Both prediction
methods work similarly within the clusters, as each method predicts the
data within the cluster with slight differences.}

@@

\includegraphics[width=1\textwidth,height=0.7\textheight]{paper_files/figure-pdf/fig-rm-lg-1.pdf}

>>>>

\caption{\label{fig-predict-two-curvy}Comparison of prediction generated
using the exiting \texttt{umap} R package's prediction method and our
method: (a) A view of the true model in projection from \(7\text{-}D\),
(b) predicted data from the \texttt{umap} prediction method, and (c)
predicted data from our method.}

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-rm-lg-1.pdf}
